Paper Analysis

### 2025-05-07 Paper_WriteUp/Paper_Plots.qmd
remove duplicate games for GMs in fig2 generation

bullet_data_gm = lichess_data_gm |> 
  mutate(Event = tolower(Event)) |>
  filter(TimeControl == "60+0", Variant == "Standard", Event == "rated bullet game")

@@

  ## A check to remove duplicated games, if they occur
  # cat("Dupes:", sum(duplicated(tidy_games_gms[1:9])), "\n", sep = " ")
  # # some players have all their games double recorded for some reason
  # tidy_games_gms <- tidy_games_gms[!duplicated(tidy_games_gms[1:9]), ] # remove duplicate rows

>>>>

bullet_data_gm = lichess_data_gm |> 
  mutate(Event = tolower(Event)) |>
  filter(TimeControl == "60+0", Variant == "Standard", Event == "rated bullet game") %>%
  distinct()

@@
